### 2018-05-16 Sections/economics_of_the_quantum_internet.tex
Started quant coin section

>>>>

%
% QuantCoin - A Quantum Computation-Backed Cryptocurrency
%

\subsection{QuantCoin\texttrademark --- A quantum computation-backed cryptocurrency}

\comment{Thus with this sequence the execution of the QC is equivalent to mining, where the verification protocol acts as the proof of work. The protocol acts as a currency converter, allowing Alice to convert dollars into coins.

In an efficient market we have the relationship:

(Dollar value of a QuantCoin) + (cash paid by Alice for execution) = (Dollar value of cost associated with physically executing the protocol on the QC by Bob).

Alternately we could replace dollars with any other asset or existing QuantCoins. In the latter case one would have relationships like:

(value of QuantCoin) =  (Dollar value of cost associated with executing the protocol on the QC by Bob) / 2.

This represents expansion in the money supply associated with each successful computation.}

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantCoin($\hat{U}_\text{comp}$, blockchain, data, reward):
\begin{enumerate}
	\item Alice possesses the raw $data$ she would like computed upon, as well as a $reward$ to pay for its processing (in arbitrary units). This could be in the form of QuantCoins, dollars, or other assets of monetary value.
	\item Bob possesses the universal quantum computer, which implements $\hat{U}_\text{comp}$.
	\item Alice encrypts her data using either homomorphic encryption, or a blind quantum computing protocol,
		\begin{align}
			encryptedInput = homoEncrypt(data)
		\end{align}
	\item Alice commits the $encryptedInput$ to the public $blockchain$,
	\begin{align}
	blockchain.commit(encryptedInput)	
	\end{align}
	\item Alice pays Bob the $reward$ to process her data.
	\item Bob processes the $encryptedInput$ on his quantum computer,
	\begin{align}
		encryptedOutput = \hat{U}_\text{comp}(encryptedInput)
	\end{align}
	\item Bob commits the encrypted output data to the public blockchain,
	\begin{align}
	blockchain.commit(encryptedOutput)	
	\end{align}
	\item Alice and Bob execute a verification protocol,
	\begin{align}
	proof = verify(encryptedOutput)	
	\end{align}
	\item The $proof$ is committed to the $blockchain$ (as is every step of the proof if it is an interactive one).
	\item The $blockchain$ network inspects that the verification is valid.
	\item If it is valid, the $blockchain$ cryptographically hashes the data and proof, encapsulating it into a QuantCoin\texttrademark token, which is given to Bob.
\end{enumerate}}}}
\caption{A rough high-level outline for how a quantum computation-backed cryptocurrency might be implemented. We have abstracted away the underlying Blockchain protocol, interfacing with it using of a high-level API, so as to abstract away the underlying Blockchain technology, which is liable to change substantially in the coming years -- it might even be a natively quantum Blockchain. We similarly call upon verification subroutines using a high-level implementation-dependent API.} \label{alg:quant_coin}
\end{table}

### 2018-05-16 Sections/essay_quantcoin.tex
Started quant coin section

\subsection{QuantCoin\texttrademark -- A computation-backed cryptocurrency}\index{Computation-backed currency}\index{Cryptocurrency}\index{QuantCoin\texttrademark}\label{sec:quantcoin}

>>>>

\subsection{QuantCoin\texttrademark -- A quantum computation-backed cryptocurrency}\index{Computation-backed currency}\index{Cryptocurrency}\index{QuantCoin\texttrademark}\label{sec:quantcoin}

### 2018-05-16 Sections/physical_architectures_for_quantum_computing.tex
Started quant coin section

\comment{To do: Jon Dowling. Entirely new section, not subsection of another existing section.}

\comment{This is to be an introductory review of this field, starting from the beginning. Use previous sections on KLM and optical cluster states as a guideline for level of detail. The following topics need to be included, and you're at full liberty to throw is as much other material as you think is appropriate to communicate the basic ideas of the approach.}

>>>>

\comment{To do: Jon Dowling. Entirely new section, not subsection of another existing section. You have a lot of freedom here.}

\comment{This is to be an introductory review of this field, starting from the beginning. Use previous sections on KLM and optical cluster states as a guideline for level of detail.}

\comment{A novice should be able to get up to speed on all the important basic concepts starting with no previous knowledge, modulo an understanding of mathematics and quantum mechanics.}

\comment{The following topics need to be included, and you're at full liberty to throw is as much other material as you think is appropriate to communicate the basic ideas of the approach. Feel free to deviate from this suggested structure if you have a clearer idea for structuring it.}
